### 2018-01-19 Chapters/Chapter01.tex
Update on Overleaf.

>>>>

Bitcoin provides interesting incentives to all players. On one hand, users have incentive to use Bitcoin because of the following: (i) the fees are small and does not depend on the amount being transfered -- but only in the size in bytes of the transaction --; (ii) the transfers will be confirmed in a well-known period; (iii) it is not possible to revert an already confirmed transfer, not even with a judicial order; and (iv) and the currency issuance rate is well-known and preset in Bitcoin's rules, which makes the Bitcoin supply predictable and trustworthy, different from fiat currencies which depends on decisions of their central banks -- i.e., it would be virtually impossible to face a hyper inflation in Bitcoin due to currency issuance. On the other hand, miners have incentive to mine Bitcoin because
